Changelog

### 2021-05-25 Chapter-6/Chapter-6.tex
Updates from Overleaf

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for a deep learning model. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get the correct results. The good news is that the most well-known data in machine learning is i.i.d.. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the dataset is i.i.d..

>>>>

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I applied a blackbox fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Populations) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for machine learning libraries. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get the correct results. The good news is that the most well-known data set in machine learning is i.i.d.. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. The dataset is widely used in many supervised machine learning tasks.  We believe the dataset is i.i.d..
